### 2009-10-20 doc/tech_doc/a-rex/arex_tech_doc.tex
add hed configuration info and clean up the rest

Each job gets a directory on the CE called the \emph{session directory}
(SD). Input files are gathered in the SD. The job is supposed to produce
new data files in the SD as well. The A-REX does not guarantee the
availability of any other places accessible by the job other than
SD (unless such a place is part of a requested Runtime Environment).
The SD is also the only place which is controlled by the A-REX. It
is accessible by the user from outside through the HTTP(S) protocol.
Any file created outside the SD is not controlled by the A-REX. Any
exchange of data between client and A-REX (including also program
modules) is performed via HTTP(S). An URL for accessing input/output
files is  obtained through the WS Local Information Description Interface
(LIDI) of A-REX.

@@

In full installation the A-REX and it's components support the following
data transfer protocols and corresponding URLs: \emph{ftp, gsiftp,
http, https, lfc} and \emph{rls.} For more information please see
{}``The Hosting Environment of the Advanced Resource Connector middleware''
document~\cite{hed}.

@@

For each local UNIX user listed in the A-REX configuration -- including
a generic one which covers all local user identities -- a \textit{control
directory} exists. In this directory the A-REX stores information
about jobs belonging to that user. Multiple users can share the same
\textit{control directory}. In most common configuration case A-REX
serves all users defined by Operating System and stores their control
file in same directory. To make it easier to recover in case of failure,
the A-REX stores most information in files rather than in memory.
All files belonging to the same job have names starting with \textbf{job.ID.,}
where ID is the job identifier.

@@

\begin{itemize}
\item \textit{subject} -- user certificate's subject, also known as the distinguished
name (DN)
\item \textit{starttime} -- GMT time when the job was accepted represented
in the Generalized Time format of LDAP 
\item \textit{lifetime} -- time period to preserve the SD after the job has
finished in seconds
\item \textit{cleanuptime} -- GMT time when the job should be removed from
the cluster and it's SD deleted in Generalized Time format
\item \textit{notify} -- email addresses and flags to send mail to about
the job specified status changes
\item \textit{processtime} -- GMT time when to start processing the job in
Generalized Time format
\item \textit{exectime} -- GMT time when to start job execution in Generalized
Time format
\item \textit{expiretime} -- GMT time when the credentials delegated to the
job expire in Generalized Time format
\item \textit{rerun} -- number of retries left to rerun the job
\item \textit{jobname} -- name of the job as supplied by the user
\item \textit{projectname} -- name of the project as supplied by the user
\item \textit{lrms} -- name of the LRMS backend to be used for local submission
\item \textit{queue} -- name of the queue to run the job at
\item \textit{localid} -- job id in LRMS (appears only after the job has
reached state \textbf{InLRMS})
\item \textit{globalid} -- BES ActivityIdentifier XML tree, the global
identifier of the job
\item \textit{args} -- executable name followed by a list of command-line
arguments
\item \textit{downloads} -- number of files to download into the SD before
execution
\item \textit{uploads} -- number of files to upload from the SD after execution
\item \textit{gmlog} -- directory name which holds files containing information
about the job when accessed through GridFTP interface
\item \textit{clientname} -- name (as provided by the user interface) and
IP address:port of the submitting client machine
\item \textit{clientsoftware} -- version of software used to submit the job
\item \textit{sessiondir} -- the job's SD
\item \textit{failedstate} -- state in which job failed (available only if
it is possible to restart the job)
\item \textit{jobreport} -- URL of a user requested \emph{logger service}.
The A-REX will also send job records to this service in addition to
the default logger service configured in the configuration.
\item \textit{activityid} -- Job-id of previous job in case the job has been 
resubmitted or migrated. This value can appear multiple times if a job has been 
resubmitted or migrate more than once.
\item \textit{forcemigration} -- This boolean is only used for migration of jobs.
It determines whether the job should persists if the termination of the previous 
job fails.
\end{itemize}
\end{itemize}

@@

\begin{itemize}
\item \textit{job.ID.input} -- list of input files. Each line contains 2
values separated by a space. First value contains name of the file
relative to the SD. Second value is an URL or a file description.
Example:

@@

\emph{URL} represents location from which file can be downloaded.
Each URL can contain additional options.

\textit{file description} -- {[}size]{[}.checksum].

\hspace*{1cm}\textit{size} -- size of the file in bytes.

\hspace*{1cm}\textit{checksum} -- checksum of the file identical to
the one produced by \textbf{\textit{cksum}} (1).

Both size and checksum can be left out. Special kind of file description
{*}.{*} is used to specify files which are \textbf{not} required to
exist.
\end{itemize}

@@

\begin{itemize}
\item \textit{job.ID.output} -- list of output files. Each line contains
1 or 2 values separated by a space. First value is the name of the
file relative to the SD. The second value, if present, is a URL. Supported
URLs are the same as those supported by job.ID.input.
\end{itemize}

@@

\begin{itemize}
\item \textit{job.ID.failed} -- the existence of this file marks the failure
of the job. It can also contain one or more lines of text describing
the reason of failure. Failure includes the return code different
from zero of the job itself.
\item \textit{job.ID.errors} -- this file contains the output produced by
external utilities like \textbf{\textit{downloader}}, \textbf{\textit{uploader}},
script for job submission to LRMS, etc on their stderr handle. Those
are not necessarily errors, but can be just useful information about
actions taken during the job processing. In case of problem include
content of that file while asking for help.
\item \textit{job.ID.diag} -- information about resources used during execution
of job and other information suitable for diagnostics and statistics.
It's format is similar to that of \textit{job.ID.local}. The following
names are at least defined:
\begin{itemize}
\item \textit{nodename} -- name of computing node which was used to execute
job,
\item \textit{runtimeenvironments} -- used runtime environments separated
by ';',
\item \textit{exitcode} -- numerical exit code of job,
\item \textit{frontend\_distribution} -- name and version of operating system
distribution on frontend computer,
\item \textit{frontend\_system} -- name of operating on frontend computer,
\item \textit{frontend\_subject} -- subject (DN) of certificate representing
frontend computer,
\item \textit{frontend\_ca} -- subject (DN) of issuer of certificate representing
frontend computer,
\end{itemize}
and other information provided by GNU \emph{time} utility. Note that
some implementation of \emph{time} insert unrequested information
in their output. Hence some lines can have broken format.
\item \textit{job.ID.proxy} -delegated X509 credentials.
\item \textit{job.ID.proxy.tmp} -- temporary X509 credentials with different
UNIX ownership used by processes run with effective \emph{user id}
different form job owner's \emph{id}.
\end{itemize}

@@

The A-REX can cache input files. Caching is enabled if one or more cache
directories are specified in the configuration file. The A-REX does not
cache files marked as executable in a job. Caching can also be explicitly
turned off by the user for each file by using the\textit{ cache=no}
option in the URL (for URL options read {}``Protocols, Uniform Resource
Locators (URL) and extensions supported in ARC'' \cite{urls}). The
disk space occupied by the cache is controlled by removing old files.
For more information look in section \ref{SubSection:ConfigFile}.

@@

\subsection{Administration tools}

@@

\begin{itemize}
\item \emph{cache-clean} - This tool is used periodically (every 2 minutes)
by the A-REX to keep the size of each cache within the configurated limits.
It removes files from the cache if the total size of the cache is
greater than the configured limit. It will attempt to remove files
which are not locked in order of access time, starting with the earliest,
until the size is lower than the configured lower limit. If the lower
limit cannot be reached (because too many files are locked, or other
files outside the cache are taking up space on the file system), the
tool will exit before the lower limit is reached.\\
\emph{cache-clean -h} gives a list of options. The most useful option
for administrators is \emph{-s}, which does not delete anything, but
gives summary information on the files in the cache, including information
on the ages of the files in the cache.\\
It is not recommended to run \emph{cache-clean }manually to clean
up the cache, unless it is desired to temporarily clean up the cache
with different size limits to those specified in the configuration.
\item \emph{cache-list} - This tool is used to list all files present in
each cache. It simply reads through all the \emph{.meta }files and
prints to stdout a list of all URLs stored in each cache and their
corresponding cache filename, one per line.
\end{itemize}

@@

\begin{itemize}
\item \textit{session root directory} -- This is the directory in which a
user's SDs are created. It's location is configurable per UNIX user.
Several (or even all) users may share the same session root directory.\\
The A-REX need to have permission to create new files and directories
in the session root directory. If A-REX is run under a dedicated user
account, that account needs full permissions in the \textit{session
root directory}.\\
If A-REX is run under the \emph{root} account, make sure \textit{session
root directory} resides on a file system which does not limit the
capabilities of the \emph{root} user (as does for example NFS with
\emph{root\_squash} option).\\
If there is a need to run A-REX under the \emph{root} account (to
be able to run jobs in LRMS under different users' accounts, for example)
but there is no way to provide a suitable \textit{session root directory,}
use the \emph{norootpower} command in configuration file. In that
case A-REX will use the identity of the local user to which a Grid
identity is mapped to access the \textit{session root directory}.
Hence those users will need full access there.\\
The A-REX creates SDs with proper ownership and permissions for the
local identity used to run a job. Some file systems require users
to have \emph{execute} permission on the \textit{session root directory}
in order to access any file or subdirectory there.\\
In order for jobs to access their input files, session root directories
should be shared across cluster nodes. Otherwise, LRMS-specific methods
must be used to transfer files to execution nodes. 
\end{itemize}

@@

\begin{shaded}
\verb|name=''arguments string''|
\end{shaded}
Following commands are defined:

@@

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which the notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finished (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7days for \emph{ttl} and 30 days for \emph{ttr}.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by usingon
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path} -- specifies path to the directory
in which the SD is created. If the path is {*} the default one is
used -- \textit{\$HOME/.jobs}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} - specifies
a directory to store cached data (see \ref{sec:cache}).\emph{ }Multiple
cache directories may be specified by specifying multiple \emph{cachedir}
commands. Cached data will be distributed evenly over the caches.
Specifying no \emph{cachedir }command or commands with an empty path
disables caching. Optional \textit{link\_path} specifies the path
at which \emph{path} is accessible on computing nodes, if it is different
from the path on the A-REX host. If \textit{link\_path} is set to '.'
files are not soft-linked, nor are per-job links created, but files
are copied to the session directory.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} - specifies
high and low watermarks for space used by each cache, as a percentage
of the space on the file system on which the cache directory is located.
When the max is exceeded, files will be deleted to bring the used
space down to the min level. It is a good idea to have each cache
on its own separate file system. To turn off this feature, \char`\"{}cachesize\char`\"{}
without parameters can be specified. These cache settings apply to
all caches specified by \emph{cachedir} commands.
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. Actual
number is provided in job description and defaults to 0.
\end{itemize}

@@

The A-REX service is a pluggable module of the HED. So first You need
to setup your HED -- see HED documentation.

Then You need to add A-REX to the HED configuration. Add new \verb|<Name>|
element inside \verb|<Plugins>| containing string \emph{arex}. That will
make HED load libarex plugin library.

Then add new \verb|<Service>| element with attribute \verb|name=``a-rex''|. That
will instantiate A-REX service. Now to make service accessible extend
\verb|<Plexer>| element with new \verb|<next>| referring to an id of the service.
Write \verb|<Service>| element carefully -- here is an example:

\begin{shaded}
\begin{verbatim}
    <!-- A-Rex service -->
    <Service name="a-rex" id="a-rex">
      <!-- Optional endpoint element is advised in case of multiple IP adresses -->
      <arex:endpoint>https://localhost:60000/arex</arex:endpoint>
      <!-- Use information generated by identity.map plugin or default provided below -->
      <arex:usermap><arex:defaultLocalName>nobody</arex:defaultLocalName></arex:usermap>
      <!-- grid-manager part of a-rex requires legacy configuration file.
           Use arc.conf example or write own. -->
      <arex:gmconfig>/etc/arc.conf</arex:gmconfig>
    </Service>
\end{verbatim}
\end{shaded}

@@

Use a template arc\_arex.conf or write own A-REX configuration file.
For information about format and available configuration commands
see Section~\ref{SubSection:ConfigFile}.

@@

Please read \emph{User Guide}~\cite{userguide1} for usage instructions.

>>>>

Each job gets a directory on the CE called the \emph{session
  directory} (SD). Input files are gathered in the SD. The job may
also produce new data files in the SD. The A-REX does not guarantee
the availability of any other places accessible by the job other than
SD (unless such a place is part of a requested Runtime Environment).
The SD is also the only place which is controlled by the A-REX. It is
accessible by the user from outside through the HTTP(S) protocol.  Any
file created outside the SD is not controlled by the A-REX. Any
exchange of data between client and A-REX (including also program
modules) is performed via HTTP(S). An URL for accessing input/output
files is obtained through the WS Local Information Description
Interface (LIDI) of A-REX.

@@

In full installation the A-REX and it's components support the following
data transfer protocols and corresponding URLs: \emph{ftp, gsiftp,
http, https, lfc, rls} and \emph{srm.} For more information please see
{}``The Hosting Environment of the Advanced Resource Connector middleware''
document~\cite{hed}.

@@

For each local UNIX user listed in the A-REX configuration -- including
a generic one which covers all local user identities -- a \textit{control
directory} exists. In this directory the A-REX stores information
about jobs belonging to that user. Multiple users can share the same
\textit{control directory}. In most common configuration case A-REX
serves all users defined by the Operating System and stores their control
files in the same directory. To make it easier to recover in case of failure,
the A-REX stores most information in files rather than in memory.
All files belonging to the same job have names starting with \textbf{job.ID.,}
where ID is the job identifier.

@@

\begin{itemize}
\item \textit{subject} -- user certificate's subject, also known as the distinguished
name (DN)
\item \textit{starttime} -- GMT time when the job was accepted represented
in the Generalized Time format of LDAP 
\item \textit{lifetime} -- time period to preserve the SD after the job has
finished in seconds
\item \textit{cleanuptime} -- GMT time when the job should be removed from
the cluster and it's SD deleted in Generalized Time format
\item \textit{notify} -- email addresses and flags to send mail to about
the job specified status changes
\item \textit{processtime} -- GMT time when to start processing the job in
Generalized Time format
\item \textit{exectime} -- GMT time when to start job execution in Generalized
Time format
\item \textit{expiretime} -- GMT time when the credentials delegated to the
job expire in Generalized Time format
\item \textit{rerun} -- number of retries left to rerun the job
\item \textit{jobname} -- name of the job as supplied by the user
\item \textit{projectname} -- name of the project as supplied by the user
\item \textit{lrms} -- name of the LRMS backend to be used for local submission
\item \textit{queue} -- name of the queue to run the job at
\item \textit{localid} -- job id in LRMS (appears only after the job has
reached state \textbf{InLRMS})
\item \textit{globalid} -- BES ActivityIdentifier XML tree, the global
identifier of the job
\item \textit{args} -- executable name followed by a list of command-line
arguments
\item \textit{downloads} -- number of files to download into the SD before
execution
\item \textit{uploads} -- number of files to upload from the SD after execution
\item \textit{gmlog} -- directory name which holds files containing information
about the job when accessed through GridFTP interface
\item \textit{clientname} -- name (as provided by the user interface) and
IP address:port of the submitting client machine
\item \textit{clientsoftware} -- version of software used to submit the job
\item \textit{sessiondir} -- the job's SD
\item \textit{failedstate} -- state in which job failed (available only if
it is possible to restart the job)
\item \textit{jobreport} -- URL of a user requested \emph{logger service}.
The A-REX will also send job records to this service in addition to
the default logger service configured in the configuration.
\item \textit{activityid} -- Job-id of previous job in case the job has been 
resubmitted or migrated. This value can appear multiple times if a job has been 
resubmitted or migrate more than once.
\item \textit{forcemigration} -- This boolean is only used for migration of jobs.
It determines whether the job should persist if the termination of the previous 
job fails.
\end{itemize}

@@

\item \textit{job.ID.input} -- list of input files. Each line contains 2
values separated by a space. First value contains name of the file
relative to the SD. Second value is a URL or a file description.
Example:

@@

A URL represents a location from which a file can be downloaded.
Each URL can contain additional options.

A file description refers to a file uploaded from the UI and consists
of {[}size]{[}.checksum] where

\hspace*{1cm}\textit{size} - size of the file in bytes.

\hspace*{1cm}\textit{checksum} - checksum of the file identical to
the one produced by \textbf{\textit{cksum}} (1).

These values are used to verify the transfer of the uploaded
file. Both size and checksum can be left out. A special kind of file
description {*}.{*} is used to specify files which are \textbf{not}
required to exist.

@@

\item \textit{job.ID.output} -- list of output files. Each line contains
1 or 2 values separated by a space. First value is the name of the
file relative to the SD. The second value, if present, is a URL. Supported
URLs are the same as those supported by job.ID.input.

@@

\item \textit{job.ID.failed} -- the existence of this file marks the failure
of the job. It can also contain one or more lines of text describing
the reason of failure. Failure includes the return code different
from zero of the job itself.
\item \textit{job.ID.errors} -- this file contains the output produced by
external utilities like \textbf{\textit{downloader}}, \textbf{\textit{uploader}},
script for job submission to LRMS, etc on their stderr handle. Those
are not necessarily errors, but can be just useful information about
actions taken during the job processing. In case of problem include
content of that file while asking for help.
\item \textit{job.ID.diag} -- information about resources used during execution
of job and other information suitable for diagnostics and statistics.
It's format is similar to that of \textit{job.ID.local}. The following
names are at least defined:
\begin{itemize}
\item \textit{nodename} -- name of computing node which was used to execute
job,
\item \textit{runtimeenvironments} -- used runtime environments separated
by ';',
\item \textit{exitcode} -- numerical exit code of job,
\item \textit{frontend\_distribution} -- name and version of operating system
distribution on frontend computer,
\item \textit{frontend\_system} -- name of operating on frontend computer,
\item \textit{frontend\_subject} -- subject (DN) of certificate representing
frontend computer,
\item \textit{frontend\_ca} -- subject (DN) of issuer of certificate representing
frontend computer,
\end{itemize}
and other information provided by GNU \emph{time} utility. Note that
some implementation of \emph{time} insert unrequested information
in their output. Hence some lines can have broken format.
\item \textit{job.ID.proxy} -delegated X509 credentials.
\item \textit{job.ID.proxy.tmp} -- temporary X509 credentials with different
UNIX ownership used by processes run with effective \emph{user id}
different form job owner's \emph{id}.
\end{itemize}

@@

The A-REX can cache input files. Caching is enabled if one or more
cache directories are specified in the configuration file. Caching can
also be explicitly turned off by the user for each file by using
the\textit{ cache=no} option in the URL (for URL options read
{}``Protocols, Uniform Resource Locators (URL) and extensions
supported in ARC'' \cite{urls}). The disk space occupied by the cache
is controlled by removing old files.  For more information on
configuration look in section \ref{SubSection:ConfigFile}.

@@

\subsection{Cache Administration}

The cache is cleaned automatically periodically (every 2 minutes) by
the A-REX to keep the size of each cache within the configured limits.
Files are removed from the cache if the total size of the cache is
greater than the configured limit. Files which are not locked are
removed in order of access time, starting with the earliest, until the
size is lower than the configured lower limit. If the lower limit
cannot be reached (because too many files are locked, or other files
outside the cache are taking up space on the file system), the
cleaning will stop before the lower limit is reached.

Since the limits on cache size are given as a percentage of space used
on the filesystem on which the cache is located, it is recommended
that each cache has its own dedicated file system. If the cache shares
space with other data on a file system, changes in the amount of
non-cache data will result in changes in the available cache space.

With large caches mounted over NFS and an A-REX heavily loaded with
data transfer processes, cache cleaning can become slow, leading to
caches filling up beyond their configured limits. For performance
reasons it may be advantageous to disable cache cleaning by the A-REX,
and run the \emph{cache-clean} tool independently on the machine
hosting the file system.

@@

\begin{itemize}
\item \emph{cache-clean} - This tool is used periodically by the A-REX to
  keep the size of each cache within the configured
  limits.\\
  \emph{cache-clean -h} gives a list of options. The most
  useful option for administrators is \emph{-s}, which does not delete
  anything, but gives summary information on the files in the cache,
  including information on the ages of the files in the cache.\\
  It is not recommended to run \emph{cache-clean} manually to clean up
  the cache, unless it is desired to temporarily clean up the cache with
  different size limits to those specified in the configuration, or to
  improve performance by running it on the file system's local node as
  mentioned above.
\item \emph{cache-list} - This tool is used to list all files present
  in each cache. It simply reads through all the \emph{.meta }files
  and prints to stdout a list of all URLs stored in each cache and
  their corresponding cache filename, one per line.
\end{itemize}

@@

\begin{itemize}
\item \textit{session root directory} -- This is the directory in which a
user's SDs are created. It's location is configurable per UNIX user.
Several (or even all) users may share the same session root directory.\\
The A-REX needs to have permission to create new files and directories
in the session root directory. If A-REX is run under a dedicated user
account, that account needs full permissions in the \textit{session
root directory}.\\
If A-REX is run under the \emph{root} account, make sure \textit{session
root directory} resides on a file system which does not limit the
capabilities of the \emph{root} user (as does for example NFS with
\emph{root\_squash} option).\\
If there is a need to run A-REX under the \emph{root} account (to
be able to run jobs in LRMS under different users' accounts, for example)
but there is no way to provide a suitable \textit{session root directory,}
use the \emph{norootpower} command in configuration file. In that
case A-REX will use the identity of the local user to which a Grid
identity is mapped to access the \textit{session root directory}.
Hence those users will need full access there.\\
The A-REX creates SDs with proper ownership and permissions for the
local identity used to run a job. Some file systems require users
to have \emph{execute} permission on the \textit{session root directory}
in order to access any file or subdirectory there.\\
In order for jobs to access their input files, session root directories
should be shared across cluster nodes. Otherwise, LRMS-specific methods
must be used to transfer files to execution nodes. 
\end{itemize}

@@

\begin{shaded}
\verb|name=``arguments string''|
\end{shaded}
Following commands are defined:

@@

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which the notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finished (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7 days for \emph{ttl} and 30 days for \emph{ttr}.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by usingon
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path} -- specifies path to the directory
in which the SD is created. If the path is {*} the default one is
used -- \textit{\$HOME/.jobs}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} - specifies
a directory to store cached data (see \ref{sec:cache}). Multiple
cache directories may be specified by specifying multiple \emph{cachedir}
commands. Cached files will be distributed evenly between the caches.
Specifying no \emph{cachedir }command or commands with an empty path
disables caching. Optional \textit{link\_path} specifies the path
at which \emph{path} is accessible on computing nodes, if it is different
from the path on the A-REX host. If \textit{link\_path} is set to '.'
files are not soft-linked, nor are per-job links created, but files
are copied to the session directory.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} - specifies
high and low watermarks for space used by each cache, as a percentage
of the space on the file system on which the cache directory is located.
When the max is exceeded, files will be deleted to bring the used
space down to the min level. It is a good idea to have each cache
on its own separate file system. To turn off this feature, \char`\"{}cachesize\char`\"{}
without parameters can be specified. These cache settings apply to
all caches specified by \emph{cachedir} commands.
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. Actual
number is provided in job description and defaults to 0.
\end{itemize}

@@

The A-REX service is a pluggable module of the HED, so it is first
required to set up HED configuration, and add the A-REX elements. To
add A-REX to an existing HED configuration, add a new \verb|<Name>|
element inside \verb|<Plugins>| containing the string
\emph{arex}. This will make HED load the libarex plugin library.

Then add a new \verb|<Service>| element with attribute
\verb|name="a-rex"|. That will instantiate the A-REX service. Now to
make service accessible extend the \verb|<Plexer>| element with new
\verb|<next>| referring to an id of the service. Take care to write
the \verb|<Service>| element carefully.

Here is an example of the full HED configuration file including the
A-REX service definition:

\begin{shaded}
\begin{verbatim}
<?xml version="1.0"?>
<ArcConfig
  xmlns="http://www.nordugrid.org/schemas/ArcConfig/2007"
  xmlns:tcp="http://www.nordugrid.org/schemas/ArcMCCTCP/2007"
  xmlns:arex="http://www.nordugrid.org/schemas/a-rex/Config"
>
  <!-- Common configuration of the daemon -->
  <Server>
    <PidFile>/var/run/arched.pid</PidFile>
    <Logger>
      <Level>DEBUG</Level>
      <File>/var/log/arched.log</File>
      <Backups>10</Backups>
      <Maxsize>100000000</Maxsize>
    </Logger>
  </Server>
  <!-- Where to find plugins -->
  <ModuleManager>
    <Path>/usr/local/lib/arc/</Path>
  </ModuleManager>
  <!-- Simply load all needed plugins -->
  <Plugins><Name>mcctcp</Name></Plugins>
  <Plugins><Name>mcctls</Name></Plugins>
  <Plugins><Name>mcchttp</Name></Plugins>
  <Plugins><Name>mccsoap</Name></Plugins>
  <Plugins><Name>arcpdc</Name></Plugins>
  <Plugins><Name>identitymap</Name></Plugins>
  <Plugins><Name>arex</Name></Plugins>
  <!-- Create a chain -->
  <Chain>
    <!-- TCP listening socket -->
    <Component name="tcp.service" id="tcp">
      <next id="tls"/>
      <tcp:Listen><tcp:Port>60000</tcp:Port></tcp:Listen>
    </Component>
    <!-- Transport-level security -->
    <Component name="tls.service" id="tls">
      <next id="http"/>
      <!-- Location of server's security keys -->
      <KeyPath>/etc/grid-security/hostkey.pem</KeyPath>
      <CertificatePath>/etc/grid-security/hostcert.pem</CertificatePath>
      <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
      <!-- Evaluate requestor's identity into local identity.
           Comment it if no user mapping is needed. -->
      <SecHandler name="identity.map" id="map" event="incoming">
        <!-- Safe choice if all other rules failed -->
        <PDP name="allow.pdp"><LocalName>nobody</LocalName></PDP>
      </SecHandler>
    </Component>
    <!-- HTTP processing is done here -->
    <Component name="http.service" id="http">
      <next id="soap">POST</next>
      <next id="plexer">GET</next>
      <next id="plexer">PUT</next>
    </Component>
    <!-- This one parses content into XML tree -->
    <Component name="soap.service" id="soap">
      <next id="plexer"/>
    </Component>
    <!-- Directing messages to proper service -->
    <Plexer name="plexer.service" id="plexer">
      <!-- RegExp pattern is matched to path part of endpoint.
           Unmatched part of path is propagated to service in
           PLEXER:EXTENSION attribute. -->
      <next id="a-rex">^/arex</next>
    </Plexer>
    <!-- A-Rex service -->
    <Service name="a-rex" id="a-rex">
      <!-- Optional endpoint element is advised in case of multiple IP adresses -->
      <arex:endpoint>https://localhost:60000/arex</arex:endpoint>
      <!-- Use information generated by identity.map plugin or default provided below -->
      <arex:usermap><arex:defaultLocalName>nobody</arex:defaultLocalName></arex:usermap>
      <!-- grid-manager part of a-rex requires legacy configuration file.
           Use arc.conf example or write own. -->
      <arex:gmconfig>/etc/arc.conf</arex:gmconfig>
    </Service>
  </Chain>
</ArcConfig>
\end{verbatim}
\end{shaded}

@@

For A-REX configuration, either use a template arc.conf or write a new
A-REX configuration file.  For information about format and available
configuration commands see Section~\ref{SubSection:ConfigFile}. It is
also possible to specify the A-REX configuration in XML format in the
HED configuration file, instead of a separate file. For more
information on this see the examples included in the documentation
bundled with the release.

@@

For a quick start, simply run

\begin{shaded}
\begin{verbatim}
$ARC_LOCATION/sbin/arched -c <HED configuration file>
\end{verbatim}
\end{shaded}

For more information please read the \emph{User Guide}~\cite{userguide1}.
